\textbf{Resilient Machine Learning Approaches \\ for Fast Risk Evaluation and Management \\ of Financial Portfolios and Variable Annuities}

### 2025-03-19 pre_private/pre.tex
1

% \begin{frame}{Transfer Learning for Rapid Adaptation of DNN Metamodels}

%     \textbf{Challenge:} Adapting deep neural network metamodels to changing conditions.
%     \begin{itemize}
%         \item   Retraining from scratch is computationally expensive.
%         \item   Efficient incorporation of new VA contract data.
%         \item   Balancing model accuracy and computational costs.
%     \end{itemize}

%     \textbf{Solution:} Transfer learning (TL) to develop adaptable, efficient metamodels for VA dynamic hedging.

%     \begin{itemize}
%         \item   Pre-train deep neural network on contracts with abundant simulation data.
%         \item   Fine-tune on smaller dataset of new contracts/market conditions.
%         \item   Leverages shared features between VA contracts.
%         \item   Computational savings:
%             \begin{itemize}
%                 \item   Reduced training time.
%                 \item   Fewer data points needed for good performance.
%             \end{itemize}
%     \end{itemize}

%     \note{In this project, we propose a transfer learning framework for rapid adaptation of deep neural network metamodels in VA dynamic hedging.\\ }
%     \note{The problem is the same as the previous project. We want to use deep neural network metamodels to approximate the complex simulation model that involves dynamic hedging.\\}
%     \note{The difference is that we want to use transfer learning to speed up the training process.\\}
%     \note{This can be beneficial for the practical applications.\\}
%     \note{Firstly, new VA contracts are continuously issued.\\}
%     \note{Secondly, market conditions are changing.\\}
%     \note{Thirdly, the computational budget is limited.\\}
%     \note{Transfer learning can help us to adapt to the new market conditions quickly and efficiently.\\}
%     \note{We can pre-train the deep neural network metamodel on a large dataset of VA contracts with abundant simulation data.\\}
%     \note{Then, we can fine-tune the metamodel on a smaller dataset of new VA contracts with limited data.\\}
%     \note{The data is often limited for new VA contracts as simulation is expensive to run.\\}
%     \note{The shared features between VA contracts can be leveraged to speed up the training process.\\}
%     \note{We can also transfer the knowledge to other contract types.\\}
%     \note{When a new VA contract is issued, we can use transfer learning to adapt the metamodel to the new contract quickly.\\}

>>>>

\begin{frame}{Transfer Learning for Rapid Adaptation of DNN Metamodels}

    \textbf{Use Case:} Adapting deep neural network metamodels to changing conditions.
    \begin{itemize}
        \item   Retraining from scratch is computationally expensive.
        \item   Efficient incorporation of new VA contract data.
        \item   Balancing model accuracy and computational costs.
    \end{itemize}

    \textbf{Solution:} Transfer learning (TL) to develop adaptable, efficient metamodels for VA dynamic hedging.

    \begin{itemize}
        \item   Pre-train deep neural network on contracts with abundant simulation data.
        \item   Fine-tune on smaller dataset of new contracts/market conditions.
        \item   Leverages shared features between VA contracts.
        \item   Computational savings:
            \begin{itemize}
                \item   Reduced training time.
                \item   Fewer data points needed for good performance.
            \end{itemize}
    \end{itemize}

    \note{In this project, we propose a transfer learning framework for rapid adaptation of deep neural network metamodels in VA dynamic hedging.\\ }
    \note{The problem is the same as the previous project. We want to use deep neural network metamodels to approximate the complex simulation model that involves dynamic hedging.\\}
    \note{The difference is that we want to use transfer learning to speed up the training process.\\}
    \note{This can be beneficial for the practical applications.\\}
    \note{Firstly, new VA contracts are continuously issued.\\}
    \note{Secondly, market conditions are changing.\\}
    \note{Thirdly, the computational budget is limited.\\}
    \note{Transfer learning can help us to adapt to the new market conditions quickly and efficiently.\\}
    \note{We can pre-train the deep neural network metamodel on a large dataset of VA contracts with abundant simulation data.\\}
    \note{Then, we can fine-tune the metamodel on a smaller dataset of new VA contracts with limited data.\\}
    \note{The data is often limited for new VA contracts as simulation is expensive to run.\\}
    \note{The shared features between VA contracts can be leveraged to speed up the training process.\\}
    \note{We can also transfer the knowledge to other contract types.\\}
    \note{When a new VA contract is issued, we can use transfer learning to adapt the metamodel to the new contract quickly.\\}
